Reconstructing Propositional Proofs in Type Theory

### 2017-10-23 paper/sections/limitations-type-theory.tex
[ paper ] last changes.

MISSING TEXT

@@

Therefore, one approach to guarantee a structural recursive function based on
a general recursive function $\rm{f}: \Prop \to \Prop$ is to formulate a new function $\rm{f}^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls are done on smaller arguments.

@@

Let us consider the following example to exhibit the bounded technique
mentioned above for the \fuh function. this function is used for reconstructing
the \Metis \strip inference rule in Section~\ref{sssec:strip-a-goal}.

@@

In (\ref{eq:uh-definition}), the first two equation show
call on arguments no structurally smaller.
For instance, on the first call, $φ ≡ (φ₁ ∧ φ₂) ⇒ φ₃$, the recursion
calls on the  $φ₁ ⇒ (φ₂ ⇒ φ₃)$ argument.
But this argument is not a subformula for φ.
Therefore, one way to translate $\fuh_{0}$ in (\ref{eq:uh-definition}) to type
theory is to define the a new function using the bounded technique.

@@

As we mentioned above, the natural number in the second argument of
the function stands for a complexity measure of it.

@@

...

>>>>

AGREGAR TEXTO INTRODUCTORIO

@@

Therefore, one approach to guarantee a structural recursive function based on
a general recursive function $\rm{f}:~\Prop~\to~\Prop$ is to formulate a new function $\rm{f}^{*}~:~\Prop~\to~\Nat~\to~\Prop$ where all of its recursive calls are done on smaller arguments.

@@

Let us consider the following example to exhibit the bounded technique
mentioned above for the \fuh function. This function is used for reconstructing
the \Metis \strip inference rule in Section~\ref{sssec:strip-a-goal}.

@@

In (\ref{eq:uh-definition}), the first two equation
call on arguments no structurally smaller.
For instance, on the first call, $φ ≡ (φ₁ ∧ φ₂) ⇒ φ₃$, the recursion
calls on the  $φ₁ ⇒ (φ₂ ⇒ φ₃)$ argument that is not a subformula of φ.
Therefore, one way to translate $\fuh_{0}$ to type
theory is to define a new function using a bounded recursion.

@@

We bounded the recursion calls in~(\ref{eq:uh-structured}) with \Nat type argument. This natural number represents the complexity measure of $\fuh_{0}$
function.

@@

AGREGAR TEXTO

### 2017-10-23 paper/sections/metis-language-and-proofs.tex
[ paper ] last changes.

Let us consider the following \TSTP derivation using
the customized \TSTP syntax. Note that we remove for example
empty fields in the inference information, the \verb!role! field if it is
\verb!plain! and shorten names as long as possible.

@@

@@

\begin{table}[!ht]
\label{tab:agda-metis-table}
\caption{Presentation of \Metis inference rules in type theory.}
  \begin{center}
  {\renewcommand{\arraystretch}{1.6}%
    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
    \hline
    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
    \texttt{canonicalize}
      &Normalization of the formula
      &Theorem~\ref{thm:canonicalize}
    \\
    \texttt{clausify}
      &Performs clausification
      &Theorem~\ref{thm:clausify}
    \\
    \hyperlink{atp-conjunct}{\texttt{conjunct}}
      &Takes a formula from a conjunction
      &Theorem~\ref{thm:conjunct}
    \\
    % \texttt{negate}
    %   &Negate the formula
    %   &Theorem~\ref{thm:negate}
    % \\
    \texttt{resolve}
      &A general form of the resolution theorem
      &Theorem~\ref{thm:resolve}
    \\
    \texttt{simplify}
      &Simplify definitions and theorems
      &Theorem~\ref{thm:simplify}
    \\
    \texttt{strip}
      &Strip a goal into subgoals
      &Theorem~\ref{thm:strip}
    \\[1ex]
    \hline
    \end{tabular}}
  \end{center}
\end{table}

>>>>

Let us consider the following \TSTP derivation using
the customized \TSTP syntax. Note that we remove
empty fields in the inference information, we shorten names as long as possible, and we delete the \verb!role! field when the role is
\verb!plain!.

@@

AGREGAR EL TEXTO

@@

\begin{table}[!ht]
\label{tab:agda-metis-table}
\caption{\Metis inference rules in type theory.}
  \begin{center}
  {\renewcommand{\arraystretch}{1.6}%
    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
    \hline
    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
    \texttt{canonicalize}
      &Normalization of the formula
      &Theorem~\ref{thm:canonicalize}
    \\
    \texttt{clausify}
      &Performs clausification
      &Theorem~\ref{thm:clausify}
    \\
    \hyperlink{atp-conjunct}{\texttt{conjunct}}
      &Takes a formula from a conjunction
      &Theorem~\ref{thm:conjunct}
    \\
    % \texttt{negate}
    %   &Negate the formula
    %   &Theorem~\ref{thm:negate}
    % \\
    \texttt{resolve}
      &A general form of the resolution theorem
      &Theorem~\ref{thm:resolve}
    \\
    \texttt{simplify}
      &Simplify definitions and theorems
      &Theorem~\ref{thm:simplify}
    \\
    \texttt{strip}
      &Strip a goal into subgoals
      &Theorem~\ref{thm:strip}
    \\[1ex]
    \hline
    \end{tabular}}
  \end{center}
\end{table}

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
[ paper ] last changes.

\begin{mainlemma}
  \label{lem:reorder-and-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where,
   \begin{align*}
      \begin{split}
      \label{eq:reorder-and-or}
      &\freorder_{∧∨} : \Prop \to \Prop \to \Prop\\
      &\freorder_{∧∨}~φ~ψ=
        \begin{cases}
          ψ, &\text{ if } φ ≡ ψ\\
          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁\\
             &\text{and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂\\
          φ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct_{∨}~φ~ψ &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{mainlemma}

>>>>

\begin{mainlemma}
  \label{lem:reorder-and-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where,
   \begin{align*}
      \begin{split}
      \label{eq:reorder-and-or}
      &\freorder_{∧∨} : \Prop \to \Prop \to \Prop\\
      &\freorder_{∧∨}~φ~ψ=
        \begin{cases}
          ψ, &\text{ if } φ ≡ ψ\\
          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁\\
             &\text{ and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂\\
          φ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct_{∨}~φ~ψ &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{mainlemma}
